---
title: "Function Friday #3"
author: ""
output: 
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    code_download: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      error = TRUE)
```

```{r}
library(tidyverse)   #purrr is in here
library(kableExtra)
library(googlesheets4)
library(lubridate)
gs4_deauth()
```


## purrr

Use the following data:

```{r}
mtcars
```


Question 1: Create two lists of random vectors of the same length and use map2 to get the power of the first list to the second list, by defining a function that is passed in as an argument in the mapping. 

```{r}
x <- list(10, 5, 10, 34, 35, 45, 50, 68, 80, 28)
  
y <- list(10, 2, 3, 5, 25, 10, 15, 66, 40, 80)

#map2_dbl(x, y, ~.x^.y)
Power <- function(x, y){
  return(x**y)
}
map2(x,y, Power)
```


Question 2: In the mtcars dataset, are there any cars that have a quarter mile time(qsec) faster than 20 seconds? (Hint: you may need to flatten list(mtcars$qsec)). If so, create a list of those quarter mile times.

```{r}
Q_mile_times <- list(mtcars$qsec)
Q_mile_times <- flatten_dbl(Q_mile_times)
some(Q_mile_times, function(x) x>20)
keep(Q_mile_times, function(x) x>20)
```

Question 3: Using the mtcars dataset, create a list of car names (Hint: use rownames() to pull the names since there is no variable for the names). Also create a list containing the transmission types for each car. For both lists you will need to flatten. From there, return the index of the first automatic car((0 = automatic, 1 = manual), and pluck that cars name from your list.

```{r}
names<- flatten_chr(list(rownames(mtcars)))
transmission<-(list(mtcars$am))
detect_index(flatten_dbl(transmission), function(x) x==0)
pluck(names, detect_index(flatten_dbl(transmission), function(x) x==0))              
```

## kableExtra

Make a table using the following data. Use at least one function from each section (Themes, Styles, Column / Row Specification, Grouped Columns / Rows, and HTML Only Features).

```{r}
mtcars %>% 
  kbl() %>%
  kable_material_dark() %>% 
  kable_styling(bootstrap_options = c( "bordered", "hover", "condensed"),  full_width = F, html_font = "Times New Roman") %>% 
  column_spec(2, background = "pink") %>% 
  column_spec(8, background = spec_color(1:5, option = "C", direction = -1)) %>% 
  scroll_box(width = "500px", height = "200px")
```


